\documentclass{article}
\usepackage{graphicx}
\usepackage{circuitikz}
\usepackage{amsmath}

\title{Experiment Report: Half-Wave and Bridge Wave Rectifiers}
\author{EE23BTECH11039-MAHENDRA KHINCHI}
\date{\ FEBRUARY 9,2024}

\begin{document}

\maketitle

\section{Introduction}
In this experiment, we investigate the operation and characteristics of half-wave and bridge wave rectifiers. Rectifiers are electronic devices used to convert alternating current (AC) to direct current (DC). Half-wave and bridge rectifiers are two common types used for this purpose.

\section{Aim}
The aim of this experiment is to study the operation and characteristics of half-wave and bridge wave rectifiers.

\section{Apparatus Required}
\begin{itemize}
 \item Breadboard
    \item Diodes (for bridge rectifier)
    \item Resistors
    \item Capacitors
    \item Oscilloscope
    \item Function generator
    \item Multimeter
\end{itemize}

\section{Circuit Diagrams}
\subsection{Half-Wave Rectifier}
\begin{figure}[h]
    \centering
    \begin{circuitikz}[american]
        \draw
        (0,0) to[sV] (0,3)
        (0,3) to[diode] (2,3)
        (2,3) -- (4,3)
        (4,3) to[R] (4,0)
        (4,0) -- (0,0);
    \end{circuitikz}
    \caption{Half-Wave Rectifier Circuit Diagram}
    \label{fig:half-wave}
\end{figure}

\subsection{Bridge Rectifier}
\begin{figure}[h]
 \centering
\begin{circuitikz}[scale=2]
    \draw
    (1.5,1.22) to (1.8,1.22) to (1.8,2) to (4,2)
    to (4,1.7)
    (3,1) to (3,1.7) to[Do] (4,1.7) to[Do] (5,1.7) to (5,1)
    (3,1) to (3,0.8) to[Do] (4,0.8) to[Do] (5,0.8) to (5,1)
    (3,1.3) to (2.8,1.3) to (2.8,-0.5) to (6,-0.5) 
    (5,1.3) to (6,1.3) to[R=R] (6,-0.5)
    (4,0.8) to (4,0.174) to (1.5,0.174)
    (7,1.3) to[capacitor, l=C] (7,-0.5)
    (6,1.3) to[short, -o] (7.5,1.3) node[right]{$A$}
    (6,-0.5) to[short, -o] (7.5,-0.5) node[right]{$B$}
    (1,0.7) node[transformer] (T) {Transformer};
    \draw (T.A1) ++(0,0) to[short] ++(-0.5,0) node[above]{$V_{in}$};
    \draw (T.A2) ++(0,0) to[short] ++(-0.5,0) node[below]{${GND}$};
\end{circuitikz}
\caption{Bridge Rectifier Circuit Diagram}
\label{fig:bridge}
\end{figure}

\section{Theory}
[In this experiment, we investigate the rectification of an AC signal using half-wave and bridge rectifiers. Rectification is the process of converting an alternating current (AC) into a direct current (DC) signal. Half-wave rectification only allows one half of the AC waveform to pass through, while bridge rectification allows both halves to be used. Additionally, we will observe the effect of filtering on the rectified signal.]
\section{Procedure}
\begin{enumerate}
    \item Connect the function generator output to the input of the half-wave rectifier circuit.
    \item Connect the output of the half-wave rectifier to the input of the oscilloscope and observe the waveform.
    \item Repeat steps 1-2 for the bridge rectifier circuit.
    \item Add a capacitor for filtering in both half-wave and bridge rectifier circuits.
    \item Repeat steps 1-2 for the filtered signals.
\end{enumerate}
\section{Observation}
From the observed waveforms, it can be seen that...
(Provide analysis and comparison of the waveforms, effectiveness of filtering, etc.)

\section{Conclusion}
The experiment demonstrated...
(Provide a summary of the findings and conclusions drawn from the experiment.)

\end{document}